### 2016-09-30 matrices.tex
Clarify matrices features list
I think the last items are all supposed to be related to computing inverses
(except for singular values, which was added later).

SymPy matrices support common symbolic linear algebra manipulations, including
matrix addition, multiplication, exponentiation, computing determinants,
solving linear systems, computing inverses using LU decomposition, LDL
decomposition, Gauss-Jordan elimination, Cholesky decomposition, Moore-Penrose
pseudoinverse, singular values, and adjugate matrix.

>>>>

SymPy matrices support common symbolic linear algebra manipulations, including
matrix addition, multiplication, exponentiation, computing determinants,
solving linear systems, singular values, and computing inverses using LU
decomposition, LDL decomposition, Gauss-Jordan elimination, Cholesky
decomposition, Moore-Penrose pseudoinverse, or adjugate matrices.
